---
title: "Air Pollution in India (2010)"
author: "Muhammad Mudassir Khan"
date: "November 12, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a course project for "Developing Data Products" offered by John Hopkins University through Coursera.

As a requirement for this project I have developed a Shiny WebApp which leverages the computations provided by R and presents it in HTML so that an average user can use it.

This simple app uses the air pollution data and plots average pollutant data and maps it according to its location.

## The Data

The data comes from [data.gov.in][1] and includes pollution data of $PM_{10}$,$NO_{2}$ and $SO_{2}$ for cities all over India.
```{r}
air <- readRDS("data.Rda")
```

```{r,echo=TRUE}
str(air[1:9])
```


## How It Works!

The app is simple and easy to use. You can see the geomapped data for pollution averages in major Indian Cities.

- Select the pollutant you want to see the stats on.

- Zoom in if you want to select a particular city.

- Click on the colored circles to see the average pollution ($\mu$g/$m^3$) data for that city.

## Give It A Try!

- Air Pollution Visualization App

https://mudassirkhan19.shinyapps.io/airpollution10/

- Source Code

https://github.com/mudassirkhan19/developingdataproducts/tree/gh-pages/Shiny_proj/AirPollution10

[1]: https://data.gov.in/resources/city-and-location-wise-ambient-air-quality-year-2010/download